Boosted Regression Trees for Predictive Auto-Tuning

### 2011-12-14 paper/draft1.tex
Minor wording edits

The empirical approach is very sensitive to the choice of instrumented
optimizations \emph{and} to the search method. The size of the search space is
often so large that the current best empirical auto-tuners typically only consider
highly-specialized functions with a limited set of code transformations and
compiler options, on a limited set of input domains \citep{ganapathi2009case}. Although
searches for good code configurations in highly-discontinuous spaces can
be made ``embarrassingly'' parallel, and thus benefit from parallel execution across many devices, it remains a prohibitively
expensive combinatorial optimization problem, as many variants of the code must
generated, compiled, and benchmarked on specific input domains with meaningful
statistics (that may require multiple runs). Consequently, most proposed
methods prune the space with hard-coded heuristics that offer little
generalization guarantees. This has been the main drawback of the empirical
approach compared to the model-driven approach where good code configurations
can be directly derived from the analytical model.

>>>>

The empirical approach is very sensitive to the choice of instrumented
optimizations \emph{and} to the search method. The size of the search space is
often so large that the current best empirical auto-tuners typically only consider
highly-specialized functions with a limited set of code transformations and
compiler options, on a limited set of input domains \citep{ganapathi2009case}. Although
searches for good code configurations in highly-discontinuous spaces can
be made ``embarrassingly'' parallel, and thus benefit from parallel execution across many devices, it remains a prohibitively
expensive combinatorial optimization problem, as many variants of the code must
generated, compiled, and benchmarked on specific input domains with meaningful
statistics (that may require multiple runs). Consequently, most proposed
methods prune the space with hard-coded heuristics that offer little
generalization guarantees. This has been a key drawback of the empirical
approach as compared to the model-driven approach, where good code configurations
can be directly derived from the analytical model.
